---
title: "Homework 5"
author: Sanjana Batabyal 
output: github_document
---

This is my solution to Homework 5.

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(1)
```

## Problem 1
Getting the data from the csv file downloaded from GitHub. Cleaning the data, creating a "resolved" variable, and creating a "city_state" variable.
```{r}
homicide=
  read_csv("data/homicide-data.csv") %>%
  mutate(
    city_state=str_c(city, state, sep="_"),
    resolved=case_when(
    disposition=="Closed without arrest" ~ "unsolved",
    disposition=="Closed by arrest" ~ "solved",
    disposition=="Open/No arrest" ~ "unsolved")
  ) %>%
  select(city_state, resolved) %>%
  filter(city_state != "Tulsa_AL")
```
The raw data comes from the Washington Post and contains detailed information about the homicides in 50 U.S. cities from 2012 to 2017. The dataset contains `r nrow(homicide)` rows. The data contains information on the location of the homicide; the name of the victim; his/her race, age, and ex; and the conclusion of the case (whether it was resolved or not or if it is still open).

Filtering the data to group total number of homicides and total number of unsolved homicides by location.
```{r}
agg_hom=
homicide %>%
  group_by(city_state) %>%
  summarize(
    hom_tot=n(),
    hom_unsolved=sum(resolved=="unsolved"),
  )
```
Doing a prop.test on the unsolved homicides in Baltimore, MD. 
```{r}
prop.test(
  agg_hom %>% filter(city_state=="Baltimore_MD") %>% pull(hom_unsolved),
  agg_hom %>% filter(city_state=="Baltimore_MD") %>% pull(hom_tot)
) %>%
  broom::tidy()
```
Iterating such that we perform a prop.test on each city in the data set.
```{r}
hom_results=
agg_hom %>%
  mutate(
    prop_tests=map2(.x=hom_unsolved, .y=hom_tot, ~prop.test(x=.x, n=.y)),
    tidy_tests=map(.x=prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```
Plotting the results from the previous step.
```{r}
hom_results %>%
  mutate(city_state=fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x=city_state, y=estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high)) +
  theme(axis.text = element_text(angle=90, vjust=0.5, hjust=1))
```

## Problem 2
Creating a tidy dataframe using iteration in order to import and clean the datafiles. Then splitting the data set into control and experimental arms.
```{r}
p2data=
  tibble(
    path=list.files("p2data")
  ) %>%  
  mutate(
    path1=str_c("p2data/", path),
    data=map(path1, read_csv)
    ) %>% 
  unnest(data) %>%
  separate(
    path1,
    into = c(NA, "Arm", "Arm_Num", NA)
  ) %>%
  pivot_longer(
    starts_with("week"),
    names_to = "week",
    values_to = "values"
  ) %>%
  mutate(
    week = as.numeric(sub("week_", "", week))
  )
control= 
  p2data %>% 
  select(Arm, Arm_Num, week, values) %>%
  filter(Arm=="con")
experiment=
  p2data %>% 
  select(Arm, Arm_Num, week, values) %>%
  filter(Arm=="exp")
```
Creating a spaghetti plot that shows observations on each subject over time.
```{r}
spaghetti=ggplot(control, aes(x=week, y=values, group=Arm)) +
  geom_line() + 
  geom_line(data=experiment, color="blue")

spaghetti + 
  labs(
    title="Observations on Each Subject Over Time",
    subtitle="Black = Control Group, Blue = Experimental Group",
    xlab="Week",
    ylab="Observations")
```
